Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-05-14 paper/main.tex
formatting changes in manuscript

\todo[inline]{Nach wie vor recht ausführlich; Reihenfolge der subsections mag
``inkorrekt'' sein.}

% Intro
We used data from three publicly available datsets as part of the studyforrest
dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already
been used by other research groups for independent research questions before.
% used studies
We fMRI data from three different studies. The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding, nguyen2016integration}.
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}, a dataset already used by
\citep{ben2018hippocampal}.
% VIS
c) participating in a dedicated six-category
block-design visual localizer (VIS study) \citep{sengupta2016extension}, a dataset aready used by \citep{jiahui2019predicting}.

An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications \citep{hanke2014audiomovie, hanke2016simultaneous,
sengupta2016extension}. Following is a brief summary of most important aspects.

@@

\todo[inline]{inner join von AO \& AV: N=14; AO: N=19; es fehlt in beiden VP10;
Angaben zu Alter (Durchschnitt; ggf. Range) und Geschlecht sind folglich falsch
=> hier stehen lassen und unter Data erwähnen, dass die nicht benutzt wurde}
% AO study
In the AO study, 19 German native speakers (all right-handed, age 21–38 years,
mean age 26.6 years, 12 male) listened to the German audio-description
\citep{ForrestGumpGermanAD} of the movie ``Forrest Gump''
\citep{ForrestGumpMovie} as an additional audio track for visually impaired
listeners on Swiss public television.  was Germin
% AV study
In the AV study, 15 participants (21–39 years, mean age 29.4, six female) of the
prior AO study watched the audio-visual movie with dubbed German audio track
\citep{ForrestGumpDVD}.
% VIS study
In the VIS study, the same 15 participants took part in a six-category
block-design visual localizer.
% participants' health
All participants reported to have normal hearing, normal or corrected-to-normal
vision, and no known history of neurological disorders.
% compensation, consent and shit
In all both studies, participants received monetary compensation and gave
written informed consent for their participation and for public sharing of all
obtained data in anonymized form. The studies had prior approval by the Ethics
Committee of Otto-von-Guericke University of Magdeburg, Germany.

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of
the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
temporally aligned audio-description (i.e. the audio-only variant of the movie)
that was broadcast as an additional audio track for visually impaired listeners
on Swiss public television \citep{ForrestGumpGermanAD}.
% AO vs. AV: differences
The plot of the movie is already carried by an off-screen voice of the main
character Forrest Gump.  In the largely identical audio-description, a male
narrator additionally describes essential aspects of the visual scenery when
there is no off-screen voice, dialog, or other relevant auditory content.

% AO & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$2h
\citep{hanke2014audiomovie, hanke2016simultaneous}. Both stimuli were further
processed (filtering, volume adjustments) to improve audibility during MRI
scanning. Finally, each stimulus was split into eight segments of approximately
15 minutes. Except for the first movie segment, each segment started with a
snippet of at least six seconds immediately preceding the movie scene boundary
used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}.
% AV: grey bars
Black horizontal bars at the top and bottom of stimulus of the AV study were
replaced with medium-gray bars of the same size in order to increase back-
ground illumination for a more pleasant experience.

% VIS study
% picture categories
All stimuli for the VIS study were used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (matched in
luminance, size of 400 $\times$\unit[400]{px}) from each of six stimulus
categories: human faces, human bodies without heads, small objects, houses and
outdoor scenes comprising of nature and street scenes, and phase scrambled
images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.

@@

\todo[inline]{um Hinweis bzgl. AV ergänzen}

% annotation procedure
We extended a publicly available annotation of speech \citep{haeusler2020speechanno} by manually annotating the audio-description's narrator: Two persons performed a categorization of nouns embedded in sentences spoken by the narrator to describe the movie's missing visual content.

@@

% noun categorization
% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
The nouns were categorized by the clue they provide about the cinematographic
scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent
persons (female, female name; male, male name, person), a person's appearance
(face, head; body, bodypart), and a scene's inherent objects (object,
furniture). See Table \ref{tab:descr-nouns-counts} for a complete overview of all
cateogries [+++rules, counts, examples].

A preliminary annotation was performed by one person according to the rules (see
Table \ref{tab:descr-nouns-rules}). Minor corrections due to incorrectly applied
rules were by the author.

@@

\todo[inline]{irrelevantes kürzen}

In both studies, a total of 3599 volumes were recorded for each participant
(451, 441, 438, 488, 462, 439, 542, and 338 volumes for movie segment 1–8
respectively).

@@

@@

\todo[inline]{cite sengupta2016 where this was first done and described, ie same image/data was used here}

@@

\todo[inline]{subject 10 was dropped due to excessive motion: see Hanke 2016}
% data source
fMRI time series data were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data are already aligned to a subject-specific
\href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3
Tesla BOLD template} by a rigid body transformation in MCFLIRT
\citep{jenkinson2002registration} to correct for motion during scanning
\citep{sengupta2016extension}.

@@

\paragraph{audio stimulus: contrasts of parameter estimate}
\todo[inline]{Warum ist welche COPES so gemacht und warum COPE 1 die Nummer 1}
% wieso, weshalb, warum
See Table \ref{tab:ao-contrasts}

>>>>

\todo[inline]{Nach wie vor sind Teile aus den Originalstudien ausführlich}

\todo[inline]{Reihenfolge der subsections mag ``inkorrekt'' sein.}

% intro
We used data from three publicly available datsets, all being part of the
studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org})
which has already been used by other research groups for independent research
questions.
% used studies
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration}.
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}, a dataset already used by
\citep{ben2018hippocampal}.
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study) \citep{sengupta2016extension}, a dataset aready used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications \citep{hanke2014audiomovie, hanke2016simultaneous,
sengupta2016extension}. Following is a brief summary of most important aspects.

@@

\todo[inline]{inner join von AO \& AV: N=14; AO: N=19; Exklusion von VP10 kommt
unter ``Data''}
% AO study
In the AO study, 19 German native speakers (all right-handed, age 21–38 years,
mean age 26.6 years, 12 male) listened to the German audio-description
\citep{ForrestGumpGermanAD} of the movie ``Forrest Gump''
\citep{ForrestGumpMovie} as an additional audio track for visually impaired
listeners on Swiss public television.
% AV study
In the AV study, 15 participants (21–39 years, mean age 29.4, six female) of the
prior AO study watched the audio-visual movie with dubbed German audio track
\citep{ForrestGumpDVD}.
% VIS study
In the VIS study, the same 15 participants took part in a six-category
block-design visual localizer.
% participants' health
All participants reported to have normal hearing, normal or corrected-to-normal
vision, and no known history of neurological disorders.
% compensation, consent and shit
In all studies, participants received monetary compensation and gave written
informed consent for their participation and for public sharing of obtained
data in anonymized form. The studies had prior approval by the Ethics Committee
of Otto-von-Guericke University of Magdeburg, Germany.

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
audio-description (i.e. the audio-only variant of the movie) that was broadcast
as an additional audio track for visually impaired listeners on Swiss public
television \citep{ForrestGumpGermanAD}.
% AO vs. AV: differences
The plot of the movie is already carried by an off-screen voice of the main
character Forrest Gump. In the largely identical audio-description, an
additional male describes essential aspects of the visual scenery when there is
no off-screen voice, dialog, or other relevant auditory content.

% AO & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$2h \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning. Black horizontal bars at the top and bottom of
the movie were replaced with medium-gray bars of the same size in order to
increase background illumination for a more pleasant experience.
% splitting
Each stimulus was split into eight segments of approximately 15 minutes. Except
for the first movie segment, each segment started with a snippet of at least six
seconds immediately preceding the movie scene boundary used to split the
segments (see Figure 3a in \citep{hanke2014audiomovie}.

% VIS study picture categories
All stimuli for the VIS study were used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (matched in
luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
categories: human faces, human bodies without heads, small objects, houses and
outdoor scenes comprising of nature and street scenes, and phase scrambled
images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.

@@

% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted location \citep{haeusler2016cutanno}.
% AO anno
For the analysis of the AO data, we extended another publicly available
annotation of speech \citep{haeusler2020speechanno}. We manually annotated words
spoken by the audio-description's narrator:
% annotation procedure
Two persons performed a categorization of nouns embedded in sentences spoken by
the narrator to describe the movie's missing visual content.

@@

% categories Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der
% Zeit.
The nouns were categorized by the clue they provide about the cinematographic
scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent
persons (female, female name; male, male name, person), a person's appearance
(face, head; body, bodypart), and a scene's inherent objects (object,
furniture). See Table \ref{tab:descr-nouns-counts} for a complete overview of
all cateogries [+++rules, counts, examples].
% procedure
A preliminary annotation was performed by one person according to the rules (see
Table \ref{tab:descr-nouns-rules}). Minor corrections due to incorrectly applied
rules were by the author.

@@

@@

% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338 volumes for segment 1–8 respectively).

@@

\todo[inline]{motion correction \& Templateerstellung: cite sengupta2016 where this was first done and described, ie same
image/data was used here => dort finde ich nur links

https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code

https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}

@@

% data source
fMRI time series data were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data are already aligned to a subject-specific
\href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3
Tesla BOLD template} by a rigid body transformation in MCFLIRT
\citep{jenkinson2002registration} to correct for motion during scanning
\citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant was dropped to due to invalid distortion correction
during scanning of the AO stimulus

@@

\paragraph{audio stimulus: contrasts of parameter estimate}
\todo[inline]{Warum ist welche COPES so gemacht und warum COPE 1 die Nummer 1}
% wieso, weshalb, warum
We created $t$-contrasts\dots
% table reference
See Table \ref{tab:ao-contrasts}
